cardinalR: Generating interesting high-dimensional data structures

### 2025-10-22 paper-cardinalR.Rmd
Changed the original dimensions of the data

```{r sphere, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `circle`, `curvycycle`, and `clusteredspheres` data in $4\\text{-}D$. The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships."}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), and, `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="100%", fig.align='center', fig.pos="H"}

@@

```{r trefoil, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `trefoil4d` and `trefoil3d` data in $4\\text{-}D$. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space."}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `trefoil4d` (a1-a3) and `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H"}

>>>>

```{r sphere, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `circle`, `curvycycle` data in $4\\text{-}D$, and `clusteredspheres` data in $3\\text{-}D$. The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships."}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="100%", fig.align='center', fig.pos="H"}

@@

```{r trefoil, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `trefoil4d` in $4\\text{-}D$ and `trefoil3d` data in $3\\text{-}D$. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space."}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `trefoil4d` (a1-a3) and $3\\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H"}

### 2025-10-22 paper-cardinalR.tex
Changed the original dimensions of the data

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), and, `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\text{-}D$, emphasizing the effects of projection on density, continuity, and separation}\label{fig:sphere-proj}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/trefoil-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `trefoil4d` (a1-a3) and `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.}\label{fig:trefoil-proj}
\end{figure}

>>>>

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\text{-}D$, emphasizing the effects of projection on density, continuity, and separation}\label{fig:sphere-proj}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/trefoil-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, `trefoil4d` (a1-a3) and $3\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.}\label{fig:trefoil-proj}
\end{figure}
